---
title: "The Power of Compound Interest"
---

###Goal: See the power of compound interest over time.

###Product: Line graph 

###Data: Data was self generated in excel.

###Interpretation: Comparing two people. Person A saves 1000 a month under their mattress and Person B saves 100 a month and puts it into a mutual fund earning 10% annually. Although Person A benefits from a higher savings rate there reaches a point where person B takes off. If both people were saving the same amount, the power of compound interest would be even more apparent. As it stands, this grpah shows that even with a lower savings rate, investing your money will net you more in the long run.

```{r load-packages, message = FALSE}
library(tidyverse)
library(readxl)
```

```{r}
Money <- read_excel("Compound interest data.xlsx")
```

```{r}
ggplot(Money, aes(x = Year)) + 
  geom_line(aes(y = No_Interest), color = "darkred") + 
  geom_line(aes(y = Compound_Interest), color="steelblue", linetype="twodash")+
  labs(title = "The Effect of Compound Interest", y = "Money" , x = "Years")
  #scale_color_manual(values = colours)
  #scale_color_manual(name = 'Saving Type', values = c('No Interest' = 'darkred', 'Compound Interest' = 'steelblue'))
  #legend(1,95 , legend = c("No Interest" , "Compound Interest") , col = c("darkred" , "steelblue" , lty = 1:2 , cex = .8))
```

