---
title: "Thesis Calculations for DES subscales"
---

###Goal: Test the hypothesis that the the belief that positive emotions can occur in negative situations (PeNS) predicts the number of positive aspects people identify. Although not hypotehsized, also tested whether the other belief scales could predict number of positive aspects.

###Product: Simple and multiple regression output

###Data: Data was collected in prolific for study 2

###Interpretation: PeNS was not a significant predictor. NePS was significant by itself. After further investigation...PeNS is a significant predictor of positive aspects when including NePS, because NePS is a suppressor.

```{r}
library(tidyverse)
library(tidymodels)
library(openintro)
library(broom)
library(MASS)
```


```{r}
data <- readr::read_csv("Data.csv")
```


```{r Testing PeNS as a predictor of positive aspects}
m_PNS = lm(TotalP ~ DES_PNS, data=data) 

summary(m_PNS)
```

###Not significant

```{r Testing NePS as a predictor of positive aspects}
m_NPS = lm(TotalP ~ DES_NPS, data=data) 

summary(m_NPS)
```

###Significant

```{r Testing Pe+Ne}

m_PeNe = lm(TotalP ~ DES_CPN, data=data) 

summary(m_PeNe)

```

###Not significant

```{r Testing all of them together}

m_DES = lm(TotalP ~ DES_CPN + DES_NPS + DES_PNS, data=data) 

summary(m_DES)

```

###Interesting...PeNS is now significant..why?


```{r Is PePNS significant controlling for Pe+NE?}
m_PeNePeNS = lm(TotalP ~ DES_CPN + DES_PNS, data=data)

summary(m_PeNePeNS)
```

###It's not Pe+NE that's suppressing PeNS


```{r Is NePS suppressing PeNS?}
m_PeNSNePS = lm(TotalP ~ DES_NPS + DES_PNS, data=data)

summary(m_PeNSNePS)
```

###It looks like NePS is suppressing some part of PeNS



